### 2009-09-09 latex/paper1/contents.tex
paper

while the network has less than n vertices:
  choose one of the operations according to probabilities (p, q, r)
  operation 1: (add a vertex with an outgoing edge)
    choose a vertex w within V according to f(x) = din + in-degree(x)
    add a new vertex v to w's module
    add an edge from v to w
  operation 2: (add a vertex with an ingoing edge)
    choose a vertex w within V according to f(x) = dout + out-degree(x)
    add a new vertex v to w's module
    add an edge from w to v
  operation 3: (add an edge between two existing vertices)
    choose a vertex v within V according to f(x) = dout + out-degree(x)
    choose a case according to probabilities (mu, 1 - mu)
    case 1: (distinct modules)
  	choose a vertex w within (other\_modules(v) - neighbors(v)) according to f(x) = din + in-degree(x)
      add an edge from v to w
    case 2: (same module)
      choose w within (same-module(v) - neighbors(v)) according to f(x) = din + in-degree(x)
      add an edge from v to w
  end

@@

while the network has less than n vertices:
  choose operation (p1, p2, p3, p4)
  operation 1: (adding a vertex with e1 edges)
    create a new vertex v and add it to a randomly chosen module
    do e1 times:
      choose a vertex w according to mbpa(v)
      add an edge from v to w
  operation 2: (adding e2 edges)
    do e2 times:
      choose a vertex v randomly
      choose a vertex w according to mbpa(v)
      add edge from v to w
  operation 3: (rewiring e3 edges)
    do e3 times:
      choose a vertex v randomly
      choose an edge e randomly within edges that start in v
      choose w according to mbpa(v)
      remove e
      add an edge from v to w
  operation 3: (removing e4 edges)
    do e4 times:
      remove and randomly chosen edge

@@

$$
\mathrm{S\mbox{-}score}(a) = \frac{
\sum_{s \in S} cor(a, s)
}{|S|} \mathrm{,}
$$

@@

\subsection{Patterns in Parameters}

@@

% External validity (EV): can it be generalized?
Structural information isn't enough for a expert do produce a
decomposition (s/he may use data such as names and external documentation).

Even when considering only structural information, is it true
that experts would find a decomposition similar to the reference decomposition
imposed by the model?

>>>>

\begin{figure*}
\begin{verbatim}
while the network has less than n vertices:
  choose one of the operations according to probabilities (p, q, r)
  operation 1: (add a vertex with an outgoing edge)
    choose a vertex w within V according to f(x) = din + in-degree(x)
    add a new vertex v to w's module
    add an edge from v to w
  operation 2: (add a vertex with an ingoing edge)
    choose a vertex w within V according to f(x) = dout + out-degree(x)
    add a new vertex v to w's module
    add an edge from w to v
  operation 3: (add an edge between two existing vertices)
    choose a vertex v within V according to f(x) = dout + out-degree(x)
    choose a case according to probabilities (mu, 1 - mu)
    case 1: (distinct modules)
  	choose a vertex w within (other\_modules(v) - neighbors(v)) according to f(x) = din + in-degree(x)
      add an edge from v to w
    case 2: (same module)
      choose w within (same-module(v) - neighbors(v)) according to f(x) = din + in-degree(x)
      add an edge from v to w
  end
\end{verbatim}
\end{figure*}

@@

\begin{figure*}
\begin{verbatim}
while the network has less than n vertices:
  choose operation (p1, p2, p3, p4)
  operation 1: (adding a vertex with e1 edges)
    create a new vertex v and add it to a randomly chosen module
    do e1 times:
      choose a vertex w according to mbpa(v)
      add an edge from v to w
  operation 2: (adding e2 edges)
    do e2 times:
      choose a vertex v randomly
      choose a vertex w according to mbpa(v)
      add edge from v to w
  operation 3: (rewiring e3 edges)
    do e3 times:
      choose a vertex v randomly
      choose an edge e randomly within edges that start in v
      choose w according to mbpa(v)
      remove e
      add an edge from v to w
  operation 3: (removing e4 edges)
    do e4 times:
      remove and randomly chosen edge
\end{verbatim}
\end{figure*}

@@

$$
\mathrm{S\mbox{-}score}(a) = \frac{
\sum_{s \in S} \mathrm{sim}(a, s)
}{|S|} \mathrm{,}
$$

@@

\subsection{Parameter-Based Classification Models}

@@

% External validity (EV): can it be generalized?

%Structural information isn't enough for a expert do produce a
%decomposition (s/he may use data such as names and external documentation). 
%
%Even when considering only structural information, is it true
%that experts would find a decomposition similar to the reference decomposition
%imposed by the model?
